### 2016-08-03 hoist.tex
formalism for partitioning candidates

We partition the list at the point where the above mentioned checks fail.
TODO: Put an example to illustrate the point.

>>>>

In order to hoist a subset of identical instructions, we partition the
list of all candidates in a way to maximise the total number of
hoistings.  By sorting the list of all the candidates in the
increasing order of their DFS-in numbers, we make sure that candidates
closer in the list have their common dominator nearby.

Essentially,
abs(DFS-in(I1) - DFS-in(I2)) < abs(DFS-in(I1) - DFS-in(I3))
=> dist(I1, nearest-common-dom(I1, I2)) <= dist(I1, nearest-common-dom(I1, I3))

This means for candidates closer to each other w.r.t. DFS numbers, we
would make fewer checks for preconditions.

We partition the list at the point where the above mentioned checks fail.

TODO: Put an example to illustrate the point.
